### 2013-07-26 paper.tex
qq git

Because the technical description of the problem statement is quite involved, we devote the entirety of section \ref{sec:prelim} to preliminaries and defer the actual problem statement to section \ref{sec:probstate}.  The results begin by solving the special case of one color completely in section \ref{sec:res_onecolor}.  In section \ref{sec:res_count_maps}, we also present a formula for the number of maps between two given bimodules.  The most interesting results are in sections \ref{sec:res_altcase} and \ref{sec:res_altrecurse}, where we investigate the case where the given string is $ststst\cdots$.  In particular, we show that the possible resulting structures is extremely limited, and provide a recursion based on these restrictions for special cases.

@@

Two maps $\MM_{\ul r}(\ul a)$ and $\MM_{\ul r}(\ul b)$ with identical tops may be composed by juxtaposing $\MM_{\ul r}(\ul a)$ with a flipped copy of $\MM_{\ul r}(\ul b)$; an example of such a composition is given in Figure~\ref{fig:example_compose}.  We will denote this product by $\MM_{\ul r}(\ul a, \ul b)$. % Then given two binary strings $\ul a$ and $\ul b$, we will let $\MM_{\ul r}(\ul a, \ul b)$ denote the product of $\MM_{\ul r}(\ul a)$ and $\MM_{\ul r}(\ul b)$ if $\Top_{\ul r} \ul a = \Top_{\ul r} \ul b$, and $0$ otherwise.

@@

\section{A Recursion for the Alternating Case}
\label{sec:res_altrecurse}
In this section we present a limited recursion for computing $\MM_{\AA_n}(\ul a, \ul b)$.  This recursion is sufficient to calculate $\MM_{\AA_n}(\ul b, \ul b)$.

\begin{proposition}
	BLAH
	\label{thm:recurse}
\end{proposition}

>>>>

Because the technical description of the problem statement is quite involved, we devote the entirety of section \ref{sec:prelim} to preliminaries and defer the actual problem statement to section \ref{sec:probstate}.  The results begin by solving the special case of one color completely in section \ref{sec:res_onecolor}.  In section \ref{sec:res_count_maps}, we also present a formula for the number of maps between two given bimodules.  The most interesting results are in sections \ref{sec:res_altcase} and \ref{sec:res_altcompute}, where we investigate the case where the given string is $ststst\cdots$.  In particular, we show that the possible resulting structures is extremely limited, and provide a recursion based on these restrictions for special cases.

@@

Two maps $\MM_{\ul r}(\ul a)$ and $\MM_{\ul r}(\ul b)$ with identical tops may be composed by juxtaposing $\MM_{\ul r}(\ul a)$ with a flipped copy of $\MM_{\ul r}(\ul b)$; an example of such a composition is given in Figure~\ref{fig:example_compose}.  We will denote this product by $\MM_{\ul r}(\ul a, \ul b)$.  If the two half-maps are not compatible -- i.e. $\Top_{\ul r} \ul a \neq \Top_{\ul r} \ul b$ -- then we will simply treat the product as the zero map.  % Then given two binary strings $\ul a$ and $\ul b$, we will let $\MM_{\ul r}(\ul a, \ul b)$ denote the product of $\MM_{\ul r}(\ul a)$ and $\MM_{\ul r}(\ul b)$ if $\Top_{\ul r} \ul a = \Top_{\ul r} \ul b$, and $0$ otherwise.

@@

\section{Computations for the Alternating Case}
\label{sec:res_altcompute}
We now turn to using the tools developed in section \ref{sec:res_altcase} in order to compute polynomials. First, we add some structure to these special cases.

\begin{corollary}
	For any binary strings $\ul a$ and $\ul b$ of length $n$
\end{corollary}<++>

In this section we present a limited recursion for computing $\MM_{\AA_n}(\ul a, \ul b)$.  This recursion is sufficient to calculate $\MM_{\AA_n}(\ul b, \ul b)$.

\begin{definition*}
	We say that two strings $\ul{r_1}$ and $\ul{r_2}$ \emph{agree in $c$} if their last characters are both $c$.
\end{definition*}
\begin{definition*}
	For a binary string $\ul r$, let $\ul r'$ be the string formed by deleting the last bit of $\ul r$.
\end{definition*}

\begin{proposition}
	Suppose $n \ge 1$ is an integer.  Let $\ul a$ and $\ul b$ be two binary strings of length $n$ which agree in the last bit, which have the same top $T = \Top_{\AA_n} \ul a = \Top_{\AA_n} \ul b$.  Suppose $M_1 = \MM_{\AA_{n-1}} (\ul a', \ul b') \neq 0$.  Then $M = \MM_{\AA_n} (\ul a, \ul b$) is nonzero, and the following recursion holds.
	\begin{enumerate}[(i)]
		\ii If $\AA_n$ and $T$ have the same last character $c$ (so $T \neq \varnothing$)
		\begin{itemize}
			\ii If $\ul a[n] = \ul[b] = 1$, then $M = M_1$.
			\ii If $\ul a[n] = \ul[b] = 0$, then $M = -f / \alpha_k$ where $f$ is the monomial in $M_1$ with the largest factor of $\alpha_k$, with any quantum numbers
		\end{itemize}<++>
	\end{enumerate}<++>
	\label{thm:recurse}
\end{proposition}
